%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Adapted for:
% Paul Kiernan (http://paulkiernan.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the
% line on which the font is used and either change it to a font included with
% your operating system or comment the line out to use the default font.

\RequirePackage{fix-cm}
\RequirePackage[l2tabu, orthodox]{nag}
\documentclass[]{deedy-resume-openfont}
\usepackage{microtype}

\begin{document}

% Header
\lastupdated
\namesection{Paul}{Kiernan}{
    \urlstyle{same}\url{http://paulynomial.com} \\
    \href{mailto:pak79@cornell.edu}{pak79@cornell.edu} | 646.369.6726
}

\begin{minipage}[t]{0.33\textwidth}

    \section{Education}
        \subsection{Cornell University}
            \descript{BS in Electrical and Computer Engineering}
            \location{May 2012 | Ithaca, NY}
            College of Engineering \\
            Conc. in Electrical Engineering \\
            Conc. in Computer Science\\
            John McMullen Dean Scholar\\
            Goldfarb Cornell Tradition Fellow\\
    \sectionsep

    \section{Links}
        Github:// \href{https://github.com/paulkiernan}{\custombold{paulkiernan}}\\
        LinkedIn:// \href{https://www.linkedin.com/pub/paul-kiernan/24/a32/470}{\custombold{paulkiernan}}\\
        Twitter:// \href{https://twitter.com/gaelic}{\custombold{@gaelic}}\\
    \sectionsep

    \section{Coursework}
        Robot Learning\\
        Operating Systems \\
        Open Source Software Engineering \\
        Unix Tools and Scripting \\
        C ++ Programming\\
        Computer Architecture\\
        Digital Systems Design Using Microcontrollers\\
        Microelectronics\\
        Embedded Systems\\
        Computerized Instrumentation Design\\
        Digital Logic Design\\
        Discrete Structures\\
        Signals \& Systems\\
        Probability and Inference\\
        Lasers and Optoelectronics\\
        Controlled Fusion\\
        %{\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst) }}} \\
    \sectionsep

    \section{Skills}
        \subsection{Programming}
        \location{Over 60,000 lines:}
            Python \\
        \location{Over 5000 lines:}
            Java \textbullet{}
            Shell \textbullet{}
            Matlab \textbullet{}
            \LaTeX\ \\
        \location{Over 1000 lines:}
            MySQL \textbullet{}
            C \textbullet{}
            C++ \textbullet{}
            Assembly \\
        \location{Familiar:}
            JavaScript \textbullet{}
            CSS \textbullet{}
            PHP \\
    \sectionsep

    \section{Interests}
        Cooking \textbullet{}
        Boxing \textbullet{}
        Particle Physics \\
        Fusion Engineering \textbullet{}
        Music \\
        Aerospace Engineering
    \sectionsep

\end{minipage}
\hfill
% COLUMN TWO
\begin{minipage}[t]{0.66\textwidth} 

    \section{Experience}

    \runsubsection{\href{http://www.moat.com/}{Moat}}
        \descript{|\hspace{1 mm} Software Developer}
        \location{May 2012 – Present | New York City, NY}
        \vspace{\topsep} % Hacky fix for awkward extra vertical space
        \begin{tightemize}
            \item
                Developed the full-stack behind Moat Pro, an enterprise
                ad-intelligence platform that allows markets to research trends
                in the online advertising industry.
            \item
                Developed network of web crawlers (Moatbots) capable of
                programmatically detecting, capturing, and indexing online
                advertisements.
            \item
                Extended Moatbots to index rich-media advertisements in
                addition to traditional Standard IAB formats.
            \item
                Extended Moatbots to include regional indexing capabilities,
                e.g.- develop a representation of the UK ad landscape by
                proxying traffic through UK servers.
            \item
                Developed ETL for consuming warehoused Moatbot data and
                transforming it into an optimized, queryable form.
            \item
                Refactored ETL to aggregate indexed results across different
                regions.
            \item
                Developed API to cache architecture for client side report
                generation.
            \item
                Developed Pyramid web application that used the client API to
                serve reports.
            \item
                Developed autocomplete service for web application that served
                as the primary means of directing site traffic.
            \item
                Developed Pyramid middleware for logging user engagement with
                the client-facing brand intelligence tool.
            \item
                Developed homebrew real-time analytics tool for consuming
                engagement data to build reports on site usage patterns and
                behaviour.
            \item
                Deployed a Jenkins continuous integration server for
                regression testing.
            \item
                Developed homebrew heterogeneous server role and configuration
                deployment system in Amazon’s EC2.
        \end{tightemize}
    \sectionsep

    \runsubsection{Cornell University}
        \descript{|\hspace{1 mm} Linux Infrastructure Consultant}
        \location{Jan 2009– May 2012 | Ithaca, NY}
        \begin{tightemize}
            \item
                Lead undergrad consultant at the Laboratory for Elementary-
                Particle Physics.
            \item
                Designed, installed, and serviced solutions for a network of
                high-performance computational nodes used in the study of beams
                and accelerators, photon science, and particle physics.
            \item
                Managed a complex network of heterogeneous Linux nodes
                responsible for serving the department’s administrative tasks.
        \end{tightemize}
    \sectionsep

    \section{Research}
        \runsubsection{Cornell Robot Learning Lab}
            \descript{|\hspace{1 mm} Undergraduate Researcher}
            \location{Jan 2011 – Mar 2011 | Ithaca, NY}
                Worked with \custombold{\href{http://www.cs.cornell.edu/~asaxena/}{
                Prof. Ashutosh Saxena}} to create a supervised learning algorithm
                for finding good object placements using point-clouds of an object
                and its surrounding area. Implemented the algorithm on an Adept
                Viper s850 robotic arm equipped with a Microsoft Kinect. SVM models
                built from our training examples attained performances in excess of
                80\% for both precision and recall on both flat and non-flat
                surface placement.
                \custombold{\href{http://www.cs.cornell.edu/courses/CS4758/2011sp/final_projects/spring_2011/Yang_Lyons_Kiernan.pdf}{Publication}}.
        \sectionsep

        \runsubsection{Cornell Space Systems Design Studio}
            \descript{|\hspace{1 mm} Power Subteam}
            \location{May 2010 – Dec 2010 | Ithaca, NY}
                Designed and fabricated the ATxmega128 based power distribution
                system for Cornell’s operationally responsive, high agility
                space imaging system codenamed 'Violet'.
    \sectionsep

    %\section{Awards}
        %\begin{tabular}{rll}
            %2014 & top 52/2500  & KPCB Engineering Fellow\\
            %2014 & 2\textsuperscript{nd} most points  & Google Code Jam, Qualification Round\\
            %2014 & 1\textsuperscript{st}/50  & Microsoft Coding Competition, Cornell\\
            %2013 & National  & Jump Trading Challenge Finalist\\
            %2013 & 7\textsuperscript{th}/120 & CS 3410 Cache Race Bot Tournament  \\
            %2012 & 2\textsuperscript{nd}/150 & CS 3110 Biannual Intra-Class Bot Tournament \\
            %2011 & National & Indian National Mathematics Olympiad (INMO) Finalist \\
        %\end{tabular}
    %\sectionsep

    %\section{Societies} 
        %\begin{tabular}{rll}
            %2014 & top 12\%ile & Tau Beta Pi Engineering Honor Society\\
            %2014 & National    & The Global Leadership and Education Forum (tGELF)\\
            %2012 & National    & Golden Key International Honor Society\\
        %\end{tabular}
    %\sectionsep

\end{minipage}
\end{document}
