\RequirePackage{fix-cm}
\RequirePackage[l2tabu, orthodox]{nag}
\documentclass[]{deedy-resume-openfont}
\usepackage{microtype}

\begin{document}

% Header
%\lastupdated
\namesection{Paul}{Kiernan}{
    \urlstyle{same}\url{http://paulynomial.com} \\
    \href{mailto:pak79@cornell.edu}{pak79@cornell.edu} \hspace{1mm}|\hspace{1mm} 646.369.6726
}

\raggedright
\vspace{1in}
\today\\
\vspace{10 mm}
Spotify USA Inc.\\
45 W. 18th Street, 7th Floor\\
New York, NY 10011\\
\vspace{10 mm}

To the Spotify hiring team,\\
\vspace{4 mm}

I am excited to apply to be a Backend Software Engineer at Spotify. Through my current position as a backend engineer with Moat, I have gained extensive experience building complex web applications that leverage many different systems and technologies in order to analyze large sets of data in a scalable way. I have spent the past two years developing the full-stack of Moat Pro, the enterprise version of moat.com, a search engine for online display ads. As one of the first engineers hired by the company, I have played a crucial role in developing all aspects of the product including a web-crawling bot responsible for collecting and indexing online display ads, to the data warehouse, ETL pipeline, client API, all the way the model-view-controllers of the user interface. Recently I developed systems to facilitate the dissemination of our bot traffic over different geographic regions with the goal of indexing display ads specific to local markets.
\vspace{4 mm}

While my time at Moat has been invaluable in developing my abilities as a backend engineer, I am looking to work on a product that aligns more with my interests. Like most music-enthusiasts moonlighting as engineers, I have tried my hand at making a web-based music player. I built a basic django + MySQL application that sourced media from S3 backups of my music library. Once I learned about Spotify and its ingenious approach to solving the problem of creating a unified, cross-device music player, I quickly scrapped my project and became a premium user. Spotify would later go on to fundamentally change the way I access and consume music. Spotify has created an incredible ecosystem of both producers and consumers of music. Your discovery features, live session recordings, and integrations with services like Songkick and DistroKid bring the cycle of music production, discovery, and performance full-circle in a single application. Spotify’s product is both conceptually revolutionary and technically impressive, and I want to be involved in growing it further.
\vspace{4 mm}

I would love to tell you more about how my experience, collaborative abilities, and unrelenting work ethic could assist in Spotify’s continued success; you can reach me at pak79@cornell.edu or (646) 369-6726. I am available to come to your offices for an interview at a time convenient for you. Thank you for your consideration.
\vspace{10 mm}

Sincerely,\\
Paul


\end{document}
